---
title: "Masters Homework 3"
author: "Fred LaPolla"
date: "7/28/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Use by() to find the average cholsterol level by hsq_1 status (e.g. hsq_1 level1: X mg; Level2: Y mg....):

```{r}

```



>- Subset to only have females (gender == "Female")

```{r}

```




>- Create a subset of males and find the median total cholesterol level

```{r}

```


>- Try to create a summary of the mean A1C using two factors, GENDER and DX_DBTS

```{r}

```

Find the class of the first three columns of data. What are they?

```{r}

```

How does R treat blank values?

What command can be used to identify where NAs are located in a column?

```{r}

```


How can you use indexing to create a subset without any NAs?

```{r}

```

How could you delete a column of data, for example, the 5th 
```{r}

```


What command would let you find a set of text in the cells of a column?

```{r}

```


Rename the HSQ1 variable to Health_Status

```{r}

```

Explore the Mutate command and create a ratio of total cholesterol divided by HDL

```{r}

```


Use the Synthetic Mass Data:

Make a subset of Patient data to have patient ID, sex/gender, race and ethnicity. 

```{r}

```

Make a subset of observation data for body weight and body height, and filter to have only the most recent of each. 

```{r}

```

Convert the body weight and height tables to wide format. 

```{r}

```

Merge the body weight and height information onto your demographic dataframe created in question one. 

```{r}

```

Calculate BMI into a new column. The equation is weight (kg)/height ^2 (m)

```{r}

```


