---
title: "Masters Homework 5"
author: "Fred LaPolla"
date: "8/11/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 




```{r}
nyc <- read.csv("https://raw.githubusercontent.com/fredlapolla/VilcekSummerDataAnalysis2024/main/NYC_HANES_DIAB.csv")
```



>- Using GGplot, make a boxplot of A1C by diabetes diagnosis. Would you assume the three groups have the same A1C level? 

```{r}

```


>- Use ggplot2 to make a scatter plot of A1C by glucose levels.

```{r}

```


>- Add coloration by gender for the above scatter plot and change the background theme to the minimal option. Change the X axis to label numbers by increments of 3. 

```{r}

```

>- Create a GGPlot chart of Lead vs. Cotinine and show two different themes for the background. 

```{r}

```

>- Make bar charts of mean Glucose level by diabetes diagnosis. Add error bars.

```{r}

```


>- Where could you go to look up other Geom shapes for different types of charts?


