---
title: "Masters Homework 4"
author: "Fred LaPolla"
date: "8/4/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





1. Why would one use a visualization for exploratory analysis?



7.2What information about the nature of our data can a histogram tell us?



3. Make a histogram on LEAD from the nyc data frame. Is it skewed? Which way? 

```{r}

```

4. Make a QQPlot to assess the normality UCREATININE. Is the distribution normal? How can you tell?

```{r}

```

5. Make a boxplot glucose levels by diabetes diagnosis:

```{r}


```

6. Make a scatterplot of total cholesterol by LDL. Does there appear to be a relationship?

```{r}

```

7. 


Pull in this data, https://raw.githubusercontent.com/fredlapolla/VilcekSummerDataAnalysis2024/master/elife-32032-fig2-data1_CSV.csv, which is from this paper:

Piechura JR, Amarnath K, O'Shea EK. Natural changes in light interact with circadian regulation at promoters to control gene expression in cyanobacteria. Elife. 2017 Dec 14;6:e32032. doi: 10.7554/eLife.32032. PMID: 29239721; PMCID: PMC5785211.

Make a heatmap of the pearson's R correlation of genes that are expressed such that the rowSums are greater than 100. 

```{r}

```


